---
title: "Analysis of Diabetes dataset"
author: "Estefania Mancini"
date: "2022-09-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

* This dataset is originally from the National Institute of Diabetes and Digestive and Kidney Diseases. 

* The objective of the dataset is to diagnostically predict whether or not a patient has diabetes, based on certain diagnostic measurements included in the dataset. 

* Several constraints were placed on the selection of these instances from a larger database. In particular, all patients here are females at least 21 years old of diabetes Indian heritage.

* I analyze this data following kaggle proposed strategy combined with winter genomics ML course

## Load required libraries

```{r libraries, message=FALSE}
library(corrplot)
library(caret)
library("e1071")
library(tree)
library(randomForest)
library(Amelia)
library(mice)
library(GGally)
```

## Load Data

```{r pressure, echo=FALSE, message=FALSE}
diabetes<-read.csv("diabetes.csv")
colnames(diabetes)
head(diabetes)
dim(diabetes)
```

## Check NAs:

```{r checkNAS, echo=FALSE, message=FALSE}
diabetesClean<-diabetes
diabetesClean[,1:8][diabetes[,1:8]==0]<- NA
diabetesClean$Outcome <- as.factor(diabetesClean$Outcome)
```

## Visualize NAs and impute:

```{r missmap, echo=FALSE, message=FALSE}
missmap(diabetesClean)
```

```{r mice, echo=FALSE, message=FALSE}
mice_complete <- mice(diabetesClean[,c(  "Glucose",
                                    "BMI", 
                                    "BloodPressure",
                                    "Pregnancies", 
                                    "SkinThickness", 
                                    "Insulin")],
  method="rf")

diabetesClean$Glucose<-  complete(mice_complete)$Glucose
diabetesClean$BMI <- complete(mice_complete)$BMI 
diabetesClean$BloodPressure<-  complete(mice_complete)$BloodPressure
diabetesClean$Pregnancies <- complete(mice_complete)$Pregnancies
diabetesClean$SkinThickness <- complete(mice_complete)$SkinThickness 
diabetesClean$Insulin <- complete(mice_complete)$Insulin
```

## Re-check NAs:

```{r recheckNAs, echo=FALSE, message=FALSE}
missmap(diabetes)
```

## Explore some variables 

###  Pregnancies

```{r numEmb, echo=FALSE, message=FALSE}
ggplot(diabetesClean, aes(x=Pregnancies, 
                     fill=Outcome, color=Outcome)) +
  geom_histogram(binwidth = 1) + 
  labs(title="Distribución de embarazos") + 
  theme_bw() 
```


##  Glucose levels

```{r glucose, echo=FALSE, message=FALSE}
ggplot(diabetesClean, aes(Glucose, colour = Outcome)) + 
  geom_freqpoly(binwidth = 1) + 
  labs(title="Distribución Glucosa") + 
  theme_bw() 
```

## Insuline

```{r insuline, echo=FALSE, message=FALSE}
ggplot(diabetesClean, aes(x=Insulin, fill=Outcome,
                     color=Outcome)) +
  geom_histogram(binwidth = 1) + 
  labs(title="Distribución de la insulina")+ theme_bw() 
```

## Blood pressure

```{r bloodPressure, echo=FALSE, message=FALSE}
ggplot(diabetesClean, aes(x=BloodPressure , col=Outcome))+ geom_freqpoly(binwidth = 1) + labs(title="Distribución de presión sanguínea") + theme_bw()

```


## Skin thickness

```{r skin, echo=FALSE, message=FALSE}
ggplot(diabetesClean, aes(x=SkinThickness, col=Outcome))+ 
  geom_freqpoly(binwidth = 1) + 
  labs(title="Distribución de grosor de piel") + theme_bw() 
```


## Analyze codependency

```{r dependency, echo=FALSE, message=FALSE}
ggpairs(diabetesClean[, -9])
```


```{r corrplot, echo=FALSE, message=FALSE}
corrplot(cor(diabetes[, -9]), type = "lower", method = "number")
```

## Preparing the DataSet 
training (0.75) / test (0.3) (Winter genomic ML II)

```{r partition, echo=FALSE, message=FALSE}
particion_diab<-createDataPartition(y=diabetesClean$Outcome,
                                    p=0.75, list = FALSE)

set_entrenamiento<-diabetesClean[particion_diab,]; dim(set_entrenamiento)
set_validacion<-diabetesClean[-particion_diab,]; dim(set_validacion)

prop.table(table(diabetesClean$Outcome)) * 100 
prop.table(table(set_entrenamiento$Outcome)) * 100 
prop.table(table(set_validacion$Outcome)) * 100 

head(set_entrenamiento)
dim(set_entrenamiento)
colnames(set_entrenamiento)

```

```{r select, echo=FALSE, message=FALSE}
x = set_entrenamiento[,-9] 
y = set_entrenamiento$Outcome 
```


```{r modelW, echo=FALSE, message=FALSE, warning=FALSE}
model <- train(x,y,'nb',
              trControl=trainControl(method='cv',number=10)) 
```

```{r confusionW, echo=FALSE, message=FALSE}
confusionMatrix(model)
```


## Preparing the DataSet (Model GLM and RF)

We divide the dataset in train (0.7) and  test (0.3)

```{r divide, echo=FALSE, message=FALSE}
set.seed(123)
n <- nrow(diabetes)
train <- sample(n, trunc(0.70*n))
diabetes$Outcome <- as.factor(diabetes$Outcome)
diabetes_training <- diabetes[train, ]
diabetes_testing <- diabetes[-train, ]
```

## Train the model (glm)

```{r train, echo=FALSE, message=FALSE}
glm_fm1 <- glm(Outcome ~., data = diabetes_training, family = binomial)
glm_fm2 <- update(glm_fm1, ~. - Triceps_Skin - Serum_Insulin - Age )
summary(glm_fm2)
```

## Plot some variables

```{r plotGlm, echo=FALSE, message=FALSE}
par(mfrow = c(2,2))
plot(glm_fm2)
```

## Test the model:

```{r testGlm, echo=FALSE, message=FALSE}
glm_probs <- predict(glm_fm2, newdata = diabetes_testing, type = "response")
glm_pred <- ifelse(glm_probs > 0.5, 1, 0)
```

# Confusion Matrix for logistic regression:

```{r confusion, echo=FALSE, message=FALSE}
table(Predicted = glm_pred, Actual = diabetes_testing$Outcome)
```

# Try model: random forest. Partition:

```{r split2, echo=FALSE, message=FALSE}
intrain <- createDataPartition(y = diabetes$Outcome, p = 0.7, list = FALSE)

train <- diabetes[intrain, ]
test <- diabetes[-intrain, ]
```

## Try model

```{r rfmodel, echo=FALSE, message=FALSE}
rf_diabetes <- randomForest(Outcome ~., data = diabetes_training, mtry = 8, ntree=50, importance = TRUE)
```

## Testing the Model

```{r rfmodeltest, echo=FALSE, message=FALSE}
rf_probs <- predict(rf_diabetes, newdata = diabetes_testing)
rf_pred <- ifelse(rf_probs > 0.5, 1, 0)
```

## Check importance:

```{r ranking, echo=FALSE, message=FALSE}
importance(rf_diabetes)
```

## Visualizing variables:

```{r visual, echo=FALSE, message=FALSE}
varImpPlot(rf_diabetes, type = 2, main = "Variable Importance",col = 'black')
```


## Eror vs no of trees grown

```{r errors, echo=FALSE, message=FALSE}
plot(rf_diabetes, main = "Error vs no. of trees grown")
```

# Analysis following Winter Genomic Course (ML part II)

