---
title: "WinterGenomics course: ML with R, part II"
author: "Estefania Mancini"
date: "2022-09-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Readme

To view in a browser: https://estepi.github.io/kaggle/

```{r loadLibraries, echo=FALSE, message=FALSE}
#install.packages("Amelia")
#install.packages("corrplot")
#install.packages("caret")
#install.packages("e1071")
#install.packages("tree")
#install.packages("randomForest")
#install.packages("mice")
#install.packages("GGally")
##############################################
#----Load libraries-----
library(corrplot)
library(caret)
library("e1071")
library(tree)
library(Amelia)
library(Amelia)
library(randomForest)
library(mice)
library(GGally)
```

## Load data:

This dataset is originally from the National Institute of Diabetes and Digestive and Kidney Diseases. The objective of the dataset is to diagnostically predict whether or not a patient has diabetes, based on certain diagnostic measurements included in the dataset. Several constraints were placed on the selection of these instances from a larger database. In particular, all patients here are females at least 21 years old of Pima Indian heritage.

```{r pressure, echo=FALSE}
diabetes<-read.csv("diabetes.csv")
colnames(diabetes)
head(diabetes)
```

  