---
title: "WinterGenomics course: ML with R, part II"
author: "Estefania Mancini"
date: "2022-09-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Readme

To view in a browser: https://estepi.github.io/kaggle/

```{r loadLibraries, echo=FALSE, message=FALSE}
#install.packages("Amelia")
#install.packages("corrplot")
#install.packages("caret")
#install.packages("e1071")
#install.packages("tree")
#install.packages("randomForest")
#install.packages("mice")
#install.packages("GGally")
##############################################
#----Load libraries-----
library(corrplot)
library(caret)
library("e1071")
library(tree)
library(Amelia)
library(Amelia)
library(randomForest)
library(mice)
library(GGally)
```

## Load data:

This dataset is originally from the National Institute of Diabetes and Digestive and Kidney Diseases. The objective of the dataset is to diagnostically predict whether or not a patient has diabetes, based on certain diagnostic measurements included in the dataset. Several constraints were placed on the selection of these instances from a larger database. In particular, all patients here are females at least 21 years old of Pima Indian heritage.
  
```{r load, echo=FALSE, message=FALSE}
diabetes<-read.csv("diabetes.csv")
colnames(diabetes)
head(diabetes)
```


## Prepare the DataSet

```{r prepare, echo=FALSE, message=FALSE}
diabetes$Outcome<-as.factor(diabetes$Outcome)
diabetes[,1:8][diabetes[,1:8]==0]<- NA
missmap(diabetes)
colnames(diabetes)
```

## Visualizando la variable de numero de embarazos 

```{r numEmb, echo=FALSE, message=FALSE}
ggplot(diabetes, aes(x=Pregnancies, 
                     fill=Outcome, color=Outcome)) +
  geom_histogram(binwidth = 1) + 
  labs(title="Distribución de embarazos") + 
  theme_bw() 
```


## Visualizando la variable de Glucosa 

```{r glucose, echo=FALSE, message=FALSE}
ggplot(diabetes, aes(Glucose, colour = Outcome)) + 
  geom_freqpoly(binwidth = 1) + 
  labs(title="Distribución Glucosa") + 
  theme_bw() 
```

## Visualizando la variable de Insulina 

```{r insuline, echo=FALSE, message=FALSE}
ggplot(diabetes, aes(x=Insulin, fill=Outcome,
                     color=Outcome)) +
  geom_histogram(binwidth = 1) + 
  labs(title="Distribución de la insulina")+ theme_bw() 
```

## IVisualizando la variable de presion sanguinea

```{r bloodPressure, echo=FALSE, message=FALSE}
ggplot(diabetes, aes(x=BloodPressure , col=Outcome))+ geom_freqpoly(binwidth = 1) + labs(title="Distribución de presión sanguínea") + theme_bw()

```


## Visualizando la variable de grosor de piel 

```{r skin, echo=FALSE, message=FALSE}
ggplot(diabetes, aes(x=SkinThickness, col=Outcome))+ 
  geom_freqpoly(binwidth = 1) + 
  labs(title="Distribución de grosor de piel") + theme_bw() 
```


## Analyze codependency

```{r dependency, echo=FALSE, message=FALSE}
ggpairs(diabetes)
```


## Construyendo el modelo

```{r seed}
set.seed(123)
```

Recomendacion del 0.7 al 0.85

```{r particion}
particion_diab<-createDataPartition(y=diabetes$Outcome,
                                    p=0.75, list = FALSE)

set_entrenamiento<-diabetes[particion_diab,]; dim(set_entrenamiento)
set_validacion<-diabetes[-particion_diab,]; dim(set_validacion)
```

## Chequear dimensiones de los datos partidos

```{r Checkpartition}
prop.table(table(diabetes$Outcome)) * 100 
prop.table(table(set_entrenamiento$Outcome)) * 100 
prop.table(table(set_validacion$Outcome)) * 100 
```


## Eliminando la variable string outcome 

```{r setx}
x =  set_entrenamiento[,-9] 
```

# Seleccionando la variable de clasificacion 

```{r sety}
y = set_entrenamiento$Outcome 
```

## Construyendo el modelo 


