---
title: "Analysis of Diabetes dataset"
author: "Estefania Mancini"
date: "2022-09-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

* This dataset is originally from the National Institute of Diabetes and Digestive and Kidney Diseases. 

* The objective of the dataset is to diagnostically predict whether or not a patient has diabetes, based on certain diagnostic measurements included in the dataset. 

* Several constraints were placed on the selection of these instances from a larger database. In particular, all patients here are females at least 21 years old of diabetes Indian heritage.

* I analyze this data following kaggle proposed strategy combined with winter genomics ML course

## Load required libraries

```{r libraries, message=FALSE}
library(corrplot)
library(caret)
library("e1071")
library(tree)
library(randomForest)
library(Amelia)
library(mice)
library(GGally)
```

## Load Data

```{r pressure, echo=FALSE, message=FALSE}
diabetes<-read.csv("diabetes.csv")
colnames(diabetes)
head(diabetes)
dim(diabetes)
```

## Check NAs:

```{r checkNAS, echo=FALSE, message=FALSE}
missmap(diabetes)
```

## Explore some variables 

```{r corrplot, echo=FALSE, message=FALSE}
corrplot(cor(diabetes[, -9]), type = "lower", method = "number")
```


## Preparing the DataSet

We divide the dataset in train (0.7) and  test (0.3)

```{r divide, echo=FALSE, message=FALSE}
set.seed(123)
n <- nrow(diabetes)
train <- sample(n, trunc(0.70*n))
diabetes$Outcome <- as.factor(diabetes$Outcome)
diabetes_training <- diabetes[train, ]
diabetes_testing <- diabetes[-train, ]
```

## Train the model (glm)

```{r train, echo=FALSE, message=FALSE}
glm_fm1 <- glm(Outcome ~., data = diabetes_training, family = binomial)
glm_fm2 <- update(glm_fm1, ~. - Triceps_Skin - Serum_Insulin - Age )
summary(glm_fm2)
```

## Plot some variables

```{r plotGlm, echo=FALSE, message=FALSE}
par(mfrow = c(2,2))
plot(glm_fm2)
```

## Test the model:

```{r testGlm, echo=FALSE, message=FALSE}
glm_probs <- predict(glm_fm2, newdata = diabetes_testing, type = "response")
glm_pred <- ifelse(glm_probs > 0.5, 1, 0)
```

# Confusion Matrix for logistic regression:

```{r confusion, echo=FALSE, message=FALSE}
table(Predicted = glm_pred, Actual = diabetes_testing$Outcome)
```

# Try model: random forest. Partition:

```{r split2, echo=FALSE, message=FALSE}
intrain <- createDataPartition(y = diabetes$Outcome, p = 0.7, list = FALSE)

train <- diabetes[intrain, ]
test <- diabetes[-intrain, ]
```

## Try model

```{r rfmodel, echo=FALSE, message=FALSE}
rf_diabetes <- randomForest(Outcome ~., data = diabetes_training, mtry = 8, ntree=50, importance = TRUE)
```

## Testing the Model

```{r rfmodeltest, echo=FALSE, message=FALSE}
rf_probs <- predict(rf_diabetes, newdata = diabetes_testing)
rf_pred <- ifelse(rf_probs > 0.5, 1, 0)
```

## Check importance:

```{r ranking, echo=FALSE, message=FALSE}
importance(rf_diabetes)
```

## Visualizing variables:

```{r visual, echo=FALSE, message=FALSE}
varImpPlot(rf_diabetes, type = 2, main = "Variable Importance",col = 'black')
```


## Eror vs no of trees grown

```{r errors, echo=FALSE, message=FALSE}
plot(rf_diabetes, main = "Error vs no. of trees grown")
```

# Analysis following Winter Genomic Course (ML part II)